Estimating survival in left filtered data

### 2022-03-04 reports/resources/sensitivity/results_5.tex
SER

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:11
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 80.00) --
	(306.77, 80.00);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,106.20) --
	(306.77,106.20);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,132.41) --
	(306.77,132.41);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 66.89) --
	(306.77, 66.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 93.10) --
	(306.77, 93.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,119.31) --
	(306.77,119.31);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,145.51) --
	( 57.06,145.51) --
	( 70.24,145.51) --
	( 83.42,143.49) --
	( 96.59,140.57) --
	(109.77,137.23) --
	(122.95,133.27) --
	(136.12,129.51) --
	(149.30,125.52) --
	(162.48,121.59) --
	(175.66,117.80) --
	(188.83,114.25) --
	(202.01,110.67) --
	(215.19,107.17) --
	(228.36,103.96) --
	(241.54,100.79) --
	(254.72, 97.64) --
	(267.89, 94.55) --
	(281.07, 91.40) --
	(294.25, 80.10);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,145.51) --
	( 57.06,145.51) --
	( 70.24,145.51) --
	( 83.42,142.63) --
	( 96.59,138.32) --
	(109.77,133.82) --
	(122.95,129.13) --
	(136.12,124.48) --
	(149.30,119.85) --
	(162.48,115.26) --
	(175.66,111.18) --
	(188.83,106.60) --
	(202.01,102.51) --
	(215.19, 98.38) --
	(228.36, 94.47) --
	(241.54, 90.74) --
	(254.72, 87.33) --
	(267.89, 83.84) --
	(281.07, 80.65) --
	(294.25, 68.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,144.56) --
	( 70.24,143.42) --
	( 83.42,142.10) --
	( 96.59,140.63) --
	(109.77,139.04) --
	(122.95,137.37) --
	(136.12,135.58) --
	(149.30,133.73) --
	(162.48,131.83) --
	(175.66,129.90) --
	(188.83,127.94) --
	(202.01,125.96) --
	(215.19,123.92) --
	(228.36,121.90) --
	(241.54,119.88) --
	(254.72,117.90) --
	(267.89,115.87) --
	(281.07,113.88) --
	(294.25,111.68);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,144.12) --
	( 70.24,142.58) --
	( 83.42,140.92) --
	( 96.59,139.08) --
	(109.77,137.15) --
	(122.95,135.15) --
	(136.12,133.02) --
	(149.30,130.80) --
	(162.48,128.55) --
	(175.66,126.21) --
	(188.83,123.90) --
	(202.01,121.53) --
	(215.19,119.13) --
	(228.36,116.72) --
	(241.54,114.27) --
	(254.72,111.80) --
	(267.89,109.40) --
	(281.07,107.01) --
	(294.25,104.48);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,142.70) --
	( 70.24,139.57) --
	( 83.42,136.17) --
	( 96.59,132.62) --
	(109.77,128.96) --
	(122.95,125.41) --
	(136.12,121.76) --
	(149.30,118.12) --
	(162.48,114.51) --
	(175.66,110.94) --
	(188.83,107.40) --
	(202.01,104.01) --
	(215.19,100.57) --
	(228.36, 97.20) --
	(241.54, 93.86) --
	(254.72, 90.72) --
	(267.89, 87.55) --
	(281.07, 84.81) --
	(294.25, 82.11);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,141.43) --
	( 70.24,137.18) --
	( 83.42,132.92) --
	( 96.59,128.48) --
	(109.77,124.05) --
	(122.95,119.80) --
	(136.12,115.50) --
	(149.30,111.19) --
	(162.48,106.97) --
	(175.66,102.71) --
	(188.83, 98.60) --
	(202.01, 94.62) --
	(215.19, 90.64) --
	(228.36, 86.73) --
	(241.54, 82.78) --
	(254.72, 78.97) --
	(267.89, 75.29) --
	(281.07, 72.11) --
	(294.25, 69.11);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 4};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 64.14) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 90.34) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,116.55) {0.9};

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 66.89) --
	( 31.37, 66.89);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 93.10) --
	( 31.37, 93.10);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,119.31) --
	( 31.37,119.31);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2022-01-19 23:23:12
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{amssymb}
\usepackage[no-math]{fontspec}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37, 83.54) --
	(306.77, 83.54);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,108.33) --
	(306.77,108.33);

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 31.37,133.12) --
	(306.77,133.12);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 71.14) --
	(306.77, 71.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37, 95.93) --
	(306.77, 95.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 31.37,120.72) --
	(306.77,120.72);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,145.51) --
	( 57.06,145.51) --
	( 70.24,145.51) --
	( 83.42,142.49) --
	( 96.59,139.06) --
	(109.77,135.47) --
	(122.95,131.49) --
	(136.12,127.87) --
	(149.30,124.21) --
	(162.48,120.53) --
	(175.66,116.85) --
	(188.83,113.27) --
	(202.01,109.91) --
	(215.19,106.65) --
	(228.36,103.65) --
	(241.54,100.68) --
	(254.72, 97.77) --
	(267.89, 95.03) --
	(281.07, 92.51) --
	(294.25, 82.50);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 43.89,145.51) --
	( 57.06,145.51) --
	( 70.24,145.51) --
	( 83.42,141.84) --
	( 96.59,136.64) --
	(109.77,131.45) --
	(122.95,126.66) --
	(136.12,121.76) --
	(149.30,117.09) --
	(162.48,112.64) --
	(175.66,108.28) --
	(188.83,104.06) --
	(202.01,100.30) --
	(215.19, 96.48) --
	(228.36, 92.84) --
	(241.54, 89.48) --
	(254.72, 86.14) --
	(267.89, 82.83) --
	(281.07, 79.97) --
	(294.25, 68.52);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,144.38) --
	( 70.24,143.15) --
	( 83.42,141.79) --
	( 96.59,140.33) --
	(109.77,138.79) --
	(122.95,137.19) --
	(136.12,135.49) --
	(149.30,133.73) --
	(162.48,131.91) --
	(175.66,130.09) --
	(188.83,128.22) --
	(202.01,126.36) --
	(215.19,124.44) --
	(228.36,122.53) --
	(241.54,120.63) --
	(254.72,118.77) --
	(267.89,116.86) --
	(281.07,114.98) --
	(294.25,112.91);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,144.03) --
	( 70.24,142.40) --
	( 83.42,140.72) --
	( 96.59,138.93) --
	(109.77,137.05) --
	(122.95,135.11) --
	(136.12,133.07) --
	(149.30,130.97) --
	(162.48,128.83) --
	(175.66,126.65) --
	(188.83,124.48) --
	(202.01,122.31) --
	(215.19,120.05) --
	(228.36,117.82) --
	(241.54,115.62) --
	(254.72,113.48) --
	(267.89,111.31) --
	(281.07,109.20) --
	(294.25,106.87);
\definecolor{drawColor}{RGB}{248,118,109}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,142.18) --
	( 70.24,138.80) --
	( 83.42,135.29) --
	( 96.59,131.77) --
	(109.77,128.23) --
	(122.95,124.82) --
	(136.12,121.35) --
	(149.30,117.91) --
	(162.48,114.48) --
	(175.66,111.10) --
	(188.83,107.75) --
	(202.01,104.56) --
	(215.19,101.34) --
	(228.36, 98.18) --
	(241.54, 95.05) --
	(254.72, 92.12) --
	(267.89, 89.13) --
	(281.07, 86.56) --
	(294.25, 84.04);
\definecolor{drawColor}{RGB}{0,191,196}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 4pt off 2pt ,line join=round] ( 43.89,145.51) --
	( 57.06,141.16) --
	( 70.24,136.67) --
	( 83.42,132.34) --
	( 96.59,128.02) --
	(109.77,123.71) --
	(122.95,119.58) --
	(136.12,115.46) --
	(149.30,111.36) --
	(162.48,107.36) --
	(175.66,103.38) --
	(188.83, 99.53) --
	(202.01, 95.88) --
	(215.19, 92.16) --
	(228.36, 88.54) --
	(241.54, 85.01) --
	(254.72, 81.71) --
	(267.89, 78.41) --
	(281.07, 75.60) --
	(294.25, 72.85);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,rotate=-90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.90] at (310.14,107.02) {Scenario 5};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (325.21,154.86);
\definecolor{drawColor}{gray}{0.20}

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 68.39) {0.7};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42, 93.18) {0.8};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 26.42,117.97) {0.9};

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 71.14) --
	( 31.37, 71.14);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62, 95.93) --
	( 31.37, 95.93);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 28.62,120.72) --
	( 31.37,120.72);
